A Formalization of Complete Discrete Valuation Rings and Local Fields

### 2023-12-12 HAL/CPP_paper_v2.tex
changed Bourbaki value group

Assume now that $R$ is any integral domain (not necessarily a DVR) and that $K$ is a field of fractions for $R$. The points of view taken in~\cite[Chapitre~I]{Ser62} and in~\cite[Chapitre~VI, \S3, n$^\circ$6]{Bou85} concerning valuations on $K$ are not identical: in the former, the valuations occurring in point~\ref{dvr_tfae:pts_val} of Theorem~\ref{thm:dvr_tfae} take values in $\ZZ\cup\{\infty\}$ (or $\wzmZZ$, up to our translation), whereas in the latter they are valued in the value group $K^\times/R^\times \cup\{\infty\}$ but under the assumption that there is an isomorphism $K^\times/R^\times\cong \ZZ$. In both cases they are called ``discrete''; they are said to be normalized, as above, when they are surjective. Often results are stated assuming that the valuation is normalized, relying on the possibility of achieving this normalization simply by rescaling, so that the theory of discrete valuations is essentially the theory of \emph{normalized} discrete valuations.

>>>>

Assume now that $R$ is any integral domain (not necessarily a DVR) and that $K$ is a field of fractions for $R$. The points of view taken in~\cite[Chapitre~I]{Ser62} and in~\cite[Chapitre~VI, \S3, n$^\circ$6]{Bou85} concerning valuations on $K$ are not identical: in the former, the valuations occurring in point~\ref{dvr_tfae:pts_val} of Theorem~\ref{thm:dvr_tfae} take values in $\ZZ\cup\{\infty\}$ (or $\wzmZZ$, up to our translation), whereas in the latter they are valued in \fil{\st{the value group} $K^\times/R^\times \cup\{\infty\}$, that translates to the value group $K/R^\times=K^\times/R^\times\cup\{0\}$ in our language,} but under the assumption that there is an isomorphism $K^\times/R^\times\cong \ZZ$. In both cases they are called ``discrete''; they are said to be normalized, as above, when they are surjective. Often results are stated assuming that the valuation is normalized, relying on the possibility of achieving this normalization simply by rescaling, so that the theory of discrete valuations is essentially the theory of \emph{normalized} discrete valuations.
